Carbonate chemistry at Ny-Ålesund

### 2021-05-14 awipev-CO2.Rmd
Working of atm CO2 time series plot

d_all <- as_tsibble(d_hour, index = datetime) #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(depth_group_pressure = ifelse( # create new variable depth
      pressure_insitu_ctd <= 2,
      1,
      ifelse(
        pressure_insitu_ctd > 2 & depth <= 4,
        3,
        ifelse(
          pressure_insitu_ctd > 4 & depth <= 6,
          5,
          ifelse(
            pressure_insitu_ctd > 6 & depth <= 8,
            7,
            ifelse(pressure_insitu_ctd > 8, 10, NA)
          )
        )
      )
    ),
    depth_group_philipp = ifelse( # create new variable depth
      depth <= 2,
      1,
      ifelse(
        depth > 2 & depth <= 4,
        3,
        ifelse(
          depth > 4 & depth <= 6,
          5,
          ifelse(
            depth > 6 & depth <= 8,
            7,
            ifelse(depth > 8, 10, NA)
          )
        )
      )
    )) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                date = d_hour$date,
                year = lubridate::year(d_hour$datetime), # year as a number
                monthd = lubridate::month(d_hour$datetime), # month as a number
                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) # abbreviated months
  )
rm(d_hour)
```

@@

# downloaded 2021-04-14
# http://ebas.nilu.no/Pages/DataSetList.aspx?key=3673A72690B343B1AEC0F1673FE8C09D
file_names <- c("atmospheric_co2_zeppelin/NO0042G.20160101000000.20180420115103.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", "atmospheric_co2_zeppelin/NO0042G.20170101000000.20180413180000.online_crds.carbon_dioxide.air.7mo.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", 
"atmospheric_co2_zeppelin/NO0042G.20180101000000.20210413133953.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", "atmospheric_co2_zeppelin/NO0042G.20190101000000.20210413133953.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", "atmospheric_co2_zeppelin/NO0042G.20200101000000.20210413000000.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas")
atm_co2_new <- NULL
year_co2 <- ymd_hm(paste0(c(2016:2020), "-01-01 00:00"))
for (i in 1:5) {
print(i)
tmp <-
  read_table2(file = paste0(path, file_names[i]),
  comment = "#",
  #skip = 182,
  col_names = FALSE,
  na = c("9999.999", "99.999", "9999.990", "9999.99"),
  ) %>%
  dplyr::mutate(co2_air = X3,
  datetime = year_co2[i] + X1*24*3600) %>% 
  dplyr::select(datetime, co2_air)
  tmp$datetime <- lubridate::round_date(tmp$datetime, unit="1 minutes")
atm_co2_new <- bind_rows(atm_co2_new, tmp)
  }
# combine the two sources of CO2 data
# the new source has missing data in 2018, so the data from the old source
# are used for 2018
atm_co2 <- dplyr::left_join(atm_co2_new, atm_co2_old, by = "datetime")
atm_co2 <- atm_co2 %>% 
  dplyr::rename(co2_air = co2_air.x, co2_air_old = co2_air.y) %>%
  dplyr::mutate(co2_air = ifelse(year(atm_co2$datetime) == 2018, co2_air_old, co2_air))
# summary(atm_co2)
zz <- as_tsibble(atm_co2) %>% 
  mutate(smoothed_co2_air = slide_dbl(co2_air, .f = mean,
                                   .before = 1, .after = 1))
ggplot(zz) +
  aes(x = time_hour, y = smoothed_temp, color = origin)

slide_dbl(~mean(.x$datetime, .x$co2_air), .before = 3, .after = 3)
  #slide_period_dbl(.x = atm_co2$co2_air, .f = mean, .i = atm_co2$datetime, .period = "month")

>>>>

d_all <- as_tibble(d_hour) #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(depth_group_pressure = ifelse( # create new variable depth
      pressure_insitu_ctd <= 2,
      1,
      ifelse(
        pressure_insitu_ctd > 2 & depth <= 4,
        3,
        ifelse(
          pressure_insitu_ctd > 4 & depth <= 6,
          5,
          ifelse(
            pressure_insitu_ctd > 6 & depth <= 8,
            7,
            ifelse(pressure_insitu_ctd > 8, 10, NA)
          )
        )
      )
    ),
    depth_group_philipp = ifelse( # create new variable depth
      depth <= 2,
      1,
      ifelse(
        depth > 2 & depth <= 4,
        3,
        ifelse(
          depth > 4 & depth <= 6,
          5,
          ifelse(
            depth > 6 & depth <= 8,
            7,
            ifelse(depth > 8, 10, NA)
          )
        )
      )
    )) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                date = d_hour$date,
                year = lubridate::year(d_hour$datetime), # year as a number
                monthd = lubridate::month(d_hour$datetime), # month as a number
                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) # abbreviated months
  )
rm(d_hour)
```

@@

# downloaded 2021-04-14
# http://ebas.nilu.no/Pages/DataSetList.aspx?key=3673A72690B343B1AEC0F1673FE8C09D
file_names <- c("atmospheric_co2_zeppelin/NO0042G.20160101000000.20180420115103.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", "atmospheric_co2_zeppelin/NO0042G.20170101000000.20180413180000.online_crds.carbon_dioxide.air.7mo.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", 
"atmospheric_co2_zeppelin/NO0042G.20180101000000.20210413133953.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", "atmospheric_co2_zeppelin/NO0042G.20190101000000.20210413133953.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", "atmospheric_co2_zeppelin/NO0042G.20200101000000.20210413000000.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas")
atm_co2_new <- NULL
year_co2 <- ymd_hm(paste0(c(2016:2020), "-01-01 00:00"))
for (i in 1:5) {
print(i)
tmp <-
  read_table2(file = paste0(path, file_names[i]),
  comment = "#",
  #skip = 182,
  col_names = FALSE,
  na = c("9999.999", "99.999", "9999.990", "9999.99"),
  ) %>%
  dplyr::mutate(co2_air = X3,
  datetime = year_co2[i] + X1*24*3600) %>% 
  dplyr::select(datetime, co2_air)
  tmp$datetime <- lubridate::round_date(tmp$datetime, unit="1 minutes")
atm_co2_new <- bind_rows(atm_co2_new, tmp)
  }
# combine the two sources of CO2 data
# the new source has missing data in 2018, so the data from the old source
# are used for 2018
atm_co2 <- dplyr::left_join(atm_co2_new, atm_co2_old, by = "datetime")
atm_co2 <- atm_co2 %>% 
  dplyr::rename(co2_air = co2_air.x, co2_air_old = co2_air.y) %>%
  dplyr::mutate(co2_air = ifelse(year(atm_co2$datetime) == 2018, co2_air_old, co2_air))
summary(atm_co2)
zz <- atm_co2 %>% 
  slide_dbl(~mean(.x$co2_air), .before = 1, .after = 1)
